Certified Knowledge Compilation \\ with Application to Verified Model Counting

### 2023-03-17 doc/mc-paper.tex
clean up and shorten Lean section
ring labeling -> ring weight function

\section{Logical Foundations}

@@

\begin{definition}[Ring Evaluation Problem]
\label{def:ring_evaluation}
  For commutative ring $\ring$, a {\em ring labeling} associates a value $w(x) \in \dset$ with
  every variable $x \in \varset$.  We then define $w(\obar{x})$ to equal $\mulident-w(x)$.

  For Boolean formula $\phi$, and ring labeling $w$, the {\em ring evaluation problem} is to compute:
  \begin{eqnarray}
    \rep(\phi, w) & = & \sum_{\alpha \in \modelset(\phi)} \;\; \prod_{\lit \in \alpha} w(\ell) \label{eqn:rep}
  \end{eqnarray}
  In this equation, sum \scalebox{0.8}{$\sum$} is computed using addition operation $\radd$, and product \scalebox{0.8}{$\prod$} is computed using multiplication operation $\rmul$.
\label{def:labeling}
\end{definition}

>>>>

\section{Logical Foundations}
\label{section:logical:foundations}

@@

\begin{definition}[Ring Evaluation Problem]
\label{def:ring_evaluation}
  For commutative ring $\ring$, a {\em ring weight function} associates a value $w(x) \in \dset$ with
  every variable $x \in \varset$.  We then define $w(\obar{x})$ to equal $\mulident-w(x)$.

  For Boolean formula $\phi$, and ring weight function $w$, the {\em ring evaluation problem} is to compute:
  \begin{eqnarray}
    \rep(\phi, w) & = & \sum_{\alpha \in \modelset(\phi)} \;\; \prod_{\lit \in \alpha} w(\ell) \label{eqn:rep}
  \end{eqnarray}
  In this equation, sum \scalebox{0.8}{$\sum$} is computed using addition operation $\radd$, and product \scalebox{0.8}{$\prod$} is computed using multiplication operation $\rmul$.
\end{definition}
